### 2018-03-14 pubs/itp-2018/sections/proof-reconstruction.tex
Review introduction Section 4

In this section, we describe our approach to reconstruct
propositional proofs. This reconstruction is a translation
process from a source system to the target system.
In our case, the system of origin, the automatic theorem prover, is
\Metis; the target system is a proof-assistant, \Agda. We choose
\Agda, but another proof-assistant with the same support of type
theory and inductive types could be used.

>>>>

In this section, we describe our approach to reconstruct proofs from
\CPL derivations generated by \Metis. This reconstruction consists of
a translation from a source system (\Metis) to the target system
(\Agda). The system of origin is the automatic theorem prover and the
target system is the proof-assistant. We choose \Agda but another
proof-assistant with the same support of type theory and inductive
types could be used \eg \Coq.
